Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
agregando sistemas

  \item [GuanZhengyi:] . We mainly used the classic BERT+BiLSTMs+CRF model architecture and replaced BERT
  with BETO as the pre-training model. BETO is a BERT model pre-training on Spanish text. And we
  add CNN before BiLSTM for further feature extraction. Our model architecture performed well in the
  training set and development set for identifying the types of entities
  uses the pre-training model BETO with stronger text feature
  representation capabilities as the feature representation layer. After reading the eHealth 2020
  papers, we fine-tuned the above architecture. We added CNN to further extract features of
  text. We regard NER as a classification problem at the token level. We combined BETO with
  CNN, BiLSTM and CRF model to extract global and local features of the text. That means we
  input these word vectors into CNN, BiLSTM and CRF to calculate the corresponding scores and
  perform entity recognition and BIO labeling.
\end{description}

>>>>

  \item [GuanZhengyi:] . We mainly used the classic BERT+BiLSTMs+CRF model architecture and replaced BERT
  with BETO as the pre-training model. BETO is a BERT model pre-training on Spanish text. And we
  add CNN before BiLSTM for further feature extraction. Our model architecture performed well in the
  training set and development set for identifying the types of entities
  uses the pre-training model BETO with stronger text feature
  representation capabilities as the feature representation layer. After reading the eHealth 2020
  papers, we fine-tuned the above architecture. We added CNN to further extract features of
  text. We regard NER as a classification problem at the token level. We combined BETO with
  CNN, BiLSTM and CRF model to extract global and local features of the text. That means we
  input these word vectors into CNN, BiLSTM and CRF to calculate the corresponding scores and
  perform entity recognition and BIO labeling.

  \item[JAD:] The model consist of identifying key-phrases
  and relations among them using a pre-defined system. It was a simple model that summarizes
  some parts of a general approach to NLP problem. The system is easy to train and test using
  cloud services like Google Colab. It did not perform very well at the competition.
  Our system is based on a pre-trained multi-lingual BERT[2] layer which pre-processes the input sentence and then feeds the generated
embeddings to the deep learning model. 
\end{description}
